---
title: "Plots for adaptive therapy with transitions"
author: "Vibishan"
date: ""
output: 
  html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(psych)
library(ggplot2)
library(patchwork)
library(latex2exp)
library(lmerTest)
library(ggbiplot)
library(emmeans)
library(readxl)
library(broom)
## setwd('~/adaptive-therapy-with-transitions/analysis/')
custom_theme <- theme(axis.ticks.y = element_line(linewidth = 1), axis.text.y = element_text(size = 20), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1), axis.text.x = element_text(size = 20), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 15), legend.title = element_text(size = 20)) +
  theme(strip.text.x = element_text(size = 15), strip.text.y = element_text(size = 15))
```


```{r data-processing, message=FALSE, warning=FALSE, echo=FALSE}
plotdf <- function(df, therapy) {
  if (therapy == 'No therapy') {
    df$Period <- Inf
  }
  
  if (!"Period" %in% names(df)) {
    df$Period <- Inf
  } else {
    df$Period <- suppressWarnings(as.numeric(df$Period))
  }
  
  df <- df %>%
    mutate(ModelType = if_else(c==d, if_else(a > 0, 'SC+Tr', 'SC'), if_else(a > 0, 'AC+Tr', 'AC'))) %>%
    mutate(Outcome = if_else(is.finite(Period), 'Cycling',
                       if_else(ResFraction > 0.15, 'Unfavourable', 'Favourable'))) %>%
    mutate(Therapy = therapy)
  
  outcomes <- df %>%
    group_by(ModelType, Therapy, Outcome) %>%
    count() %>% ungroup()
    
  return(list('df' = df, 'outcomes' = outcomes))
}
```

## No therapy

```{r data-import-notherapy}
no_therapy_r1 <- read_csv("no-therapy-outcomes-r1.csv", 
    col_types = cols(...1 = col_skip()))
no_therapy_r2 <- read_csv("no-therapy-outcomes-r2.csv", 
    col_types = cols(...1 = col_skip()))
no_therapy_r3 <- read_csv("no-therapy-outcomes-r3.csv", 
    col_types = cols(...1 = col_skip()))

df <- plotdf(no_therapy_r1, 'No therapy')
no_therapy_r1 <- df$df
no_therapy_r1$RepNum <- 1
no_therapy_outcomes_r1 <- df$outcomes
no_therapy_outcomes_r1$RepNum <- 1

df <- plotdf(no_therapy_r2, 'No therapy')
no_therapy_r2 <- df$df
no_therapy_r2$RepNum <- 2
no_therapy_outcomes_r2 <- df$outcomes
no_therapy_outcomes_r2$RepNum <- 2

df <- plotdf(no_therapy_r3, 'No therapy')
no_therapy_r3 <- df$df
no_therapy_r3$RepNum <- 3
no_therapy_outcomes_r3 <- df$outcomes
no_therapy_outcomes_r3$RepNum <- 3

no_therapy <- bind_rows(no_therapy_r1, no_therapy_r2, no_therapy_r3)
no_therapy_outcomes <- bind_rows(no_therapy_outcomes_r1, no_therapy_outcomes_r2, no_therapy_outcomes_r3)

no_therapy_outcomes_odds <- no_therapy_outcomes %>%
  pivot_wider(names_from = Outcome, values_from = n)

no_therapy_prop <- no_therapy_outcomes %>%
  pivot_wider(names_from = Outcome, values_from = n) %>%
  # RESTORED: Calculate FavProp instead of UnfavProp
  mutate(FavProp = Favourable / (Unfavourable + Favourable)) %>%
  group_by(ModelType, Therapy) %>%
  summarise(MeanFavProp = mean(FavProp),
            Propmin = MeanFavProp - sd(FavProp),
            Propmax = MeanFavProp + sd(FavProp)) %>%
  ungroup()

no_therapy_outcomes <- no_therapy_outcomes %>%
  group_by(ModelType, Therapy, Outcome) %>%
  summarise(Mean = mean(n),
            Ymin = Mean - sd(n),
            Ymax = Mean + sd(n)) %>%
  ungroup() %>%
  mutate(Outcome = factor(Outcome, levels = c("Unfavourable", "Favourable")))
```


```{r odds-proportions-plots, message=FALSE, warning=FALSE}
no_therapy_odds <- no_therapy_outcomes_odds %>%
  nest(data = -RepNum) %>%
    mutate(fit = map(data, ~ glm(cbind(Unfavourable + 0.5, Favourable + 0.5) ~ ModelType, family = binomial, data = .)),
      mean.comp = map(fit, emmeans, ~ModelType, type = 'response'),
      odds.obj = map(mean.comp, pairs, reverse = T, simple = 'ModelType'),
      odds.ratio = map(odds.obj, tidy, conf.int = FALSE)) %>%
  unnest(odds.ratio) %>%
  select(RepNum, contrast, odds.ratio) %>%
  group_by(contrast) %>%
  summarise(MeanOdds = mean(odds.ratio),
            OddsMin = MeanOdds - sd(odds.ratio),
            OddsMax = MeanOdds + sd(odds.ratio)) %>% ungroup() %>%
  filter(contrast %in% c('(AC+Tr) / AC', '(SC+Tr) / SC', 'SC / AC', '(SC+Tr) / (AC+Tr)')) %>%
  mutate(contrast = factor(contrast, levels = c('SC / AC', '(SC+Tr) / SC', '(AC+Tr) / AC', '(SC+Tr) / (AC+Tr)')))

fig.notreat.odds <- ggplot(data = no_therapy_odds, aes(y = contrast)) +
  geom_point(aes(x = MeanOdds), size = 6) +
  geom_errorbarh(aes(xmin = OddsMin, xmax = OddsMax), linewidth = 3, height = 0.3) +
  geom_vline(xintercept = 1, linewidth = 1.5, linetype = 'dashed', colour = 'red') +
  theme(axis.ticks.y = element_line(linewidth = 2.5), axis.text.y = element_text(size = 30), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 2.5), axis.text.x = element_text(size = 25), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 40), axis.title.x = element_text(size = 30)) +
  labs(y = 'Comparison', x = 'Odds ratio')
# ggsave('../figures/no-therapy/no-treatment-unfavourable-odds-ratios.png', fig.notreat.odds, dpi = 300, width = 10)

fig.notreat.popsize <- ggplot(data = no_therapy, aes(x=ModelType, y=PopSizeSS)) +
  geom_boxplot(alpha = 0.5, linewidth = 1, outliers = F) +
  stat_boxplot(geom = "errorbar", width = 0.5, position = position_dodge(0.9)) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  labs(y = 'Steady state population size')
# ggsave('../figures/no-therapy/no-treatment-ss-popsize.png', fig.notreat.popsize, dpi = 300, width = 5, height = 5)
```

```{r no-therapy-bars, message=FALSE, warning=FALSE, echo=FALSE}
fig.notreat.outcomes <- ggplot() +
  geom_bar(data = no_therapy_outcomes, aes(fill=Outcome, x=ModelType, y=Mean), position = 'fill', stat = "identity") +
  # RESTORED: Plot MeanFavProp
  geom_pointrange(data = no_therapy_prop, aes(x=ModelType, y=MeanFavProp, ymin=Propmin, ymax=Propmax), linewidth = 1.5, size = 0.8) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 15), legend.title = element_text(size = 20)) +
  scale_colour_viridis_d(begin = 0.2, end = 0.8) +
  scale_fill_viridis_d(begin = 0.2, end = 0.8) +
  labs(y = 'Proportion', x = 'Model Type')
ggsave('../figures/no-therapy/no-treatment-all-outcomes.png', fig.notreat.outcomes, dpi = 300, width=5.5, height=4)
getwd()
```

## Constant dose therapy
```{r data-import-cdt, message=FALSE, warning=FALSE}
st1_r1 <- read_csv("constant-dose/CDT-cytostatic-0.1-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st1_r1, 'Cytostatic1'); st1_r1 <- df$df; st1_r1$RepNum <- 1
st1_outcomes_r1 <- df$outcomes; st1_outcomes_r1$RepNum <- 1

st1_r2 <- read_csv("constant-dose/CDT-cytostatic-0.1-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st1_r2, 'Cytostatic1'); st1_r2 <- df$df; st1_r2$RepNum <- 2
st1_outcomes_r2 <- df$outcomes; st1_outcomes_r2$RepNum <- 2

st1_r3 <- read_csv("constant-dose/CDT-cytostatic-0.1-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st1_r3, 'Cytostatic1'); st1_r3 <- df$df; st1_r3$RepNum <- 3
st1_outcomes_r3 <- df$outcomes; st1_outcomes_r3$RepNum <- 3

st2_r1 <- read_csv("constant-dose/CDT-cytostatic-0.33-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st2_r1, 'Cytostatic2'); st2_r1 <- df$df; st2_r1$RepNum <- 1
st2_outcomes_r1 <- df$outcomes; st2_outcomes_r1$RepNum <- 1

st2_r2 <- read_csv("constant-dose/CDT-cytostatic-0.33-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st2_r2, 'Cytostatic2'); st2_r2 <- df$df; st2_r2$RepNum <- 2
st2_outcomes_r2 <- df$outcomes; st2_outcomes_r2$RepNum <- 2

st2_r3 <- read_csv("constant-dose/CDT-cytostatic-0.33-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st2_r3, 'Cytostatic2'); st2_r3 <- df$df; st2_r3$RepNum <- 3
st2_outcomes_r3 <- df$outcomes; st2_outcomes_r3$RepNum <- 3

tx1_r1 <- read_csv("constant-dose/CDT-cytotoxic-0.01-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx1_r1, 'Cytotoxic1'); tx1_r1 <- df$df; tx1_r1$RepNum <- 1
tx1_outcomes_r1 <- df$outcomes; tx1_outcomes_r1$RepNum <- 1

tx1_r2 <- read_csv("constant-dose/CDT-cytotoxic-0.01-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx1_r2, 'Cytotoxic1'); tx1_r2 <- df$df; tx1_r2$RepNum <- 2
tx1_outcomes_r2 <- df$outcomes; tx1_outcomes_r2$RepNum <- 2

tx1_r3 <- read_csv("constant-dose/CDT-cytotoxic-0.01-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx1_r3, 'Cytotoxic1'); tx1_r3 <- df$df; tx1_r3$RepNum <- 3
tx1_outcomes_r3 <- df$outcomes; tx1_outcomes_r3$RepNum <- 3

tx2_r1 <- read_csv("constant-dose/CDT-cytotoxic-0.05-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx2_r1, 'Cytotoxic2'); tx2_r1 <- df$df; tx2_r1$RepNum <- 1
tx2_outcomes_r1 <- df$outcomes; tx2_outcomes_r1$RepNum <- 1

tx2_r2 <- read_csv("constant-dose/CDT-cytotoxic-0.05-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx2_r2, 'Cytotoxic2'); tx2_r2 <- df$df; tx2_r2$RepNum <- 2
tx2_outcomes_r2 <- df$outcomes; tx2_outcomes_r2$RepNum <- 2

tx2_r3 <- read_csv("constant-dose/CDT-cytotoxic-0.05-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx2_r3, 'Cytotoxic2'); tx2_r3 <- df$df; tx2_r3$RepNum <- 3
tx2_outcomes_r3 <- df$outcomes; tx2_outcomes_r3$RepNum <- 3

cdt_df <- bind_rows(st1_r1, st1_r2, st1_r3,
                    st2_r1, st2_r2, st2_r3,
                    tx1_r1, tx1_r2, tx1_r3,
                    tx2_r1, tx2_r2, tx2_r3)

cdt_df_outcomes <- bind_rows(st1_outcomes_r1, st1_outcomes_r2, st1_outcomes_r3, 
                             st2_outcomes_r1, st2_outcomes_r2, st2_outcomes_r3,
                             tx1_outcomes_r1, tx1_outcomes_r2, tx1_outcomes_r3,
                             tx2_outcomes_r1, tx2_outcomes_r2, tx2_outcomes_r3)

# FIX 2: Removed premature ggsave here — the better fig.cdt.outcomes is built
# in the odds-ratios chunk and saved there as CDT-all-outcomes.png
fig.cdt.outcomes.simple <- ggplot(data = cdt_df_outcomes, aes(fill=Outcome, x=ModelType, y=n)) +
  geom_bar(position = 'fill', stat = "identity") +
  facet_wrap(~Therapy, nrow = 2) +
  custom_theme +
  scale_colour_viridis_d(begin = 0.2, end = 0.8) +
  scale_fill_viridis_d(begin = 0.2, end = 0.8) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = 'Proportion', x = 'Model Type')
```

```{r odds-ratios, message=FALSE, warning=FALSE}
cdt_prop <- cdt_df_outcomes %>%
  pivot_wider(names_from = Outcome, values_from = n) %>%
  # RESTORED: Calculate FavProp
  mutate(FavProp = Favourable / (Unfavourable + Favourable)) %>%
  group_by(ModelType, Therapy) %>%
  summarise(MeanFavProp = mean(FavProp),
            Propmin = MeanFavProp - sd(FavProp),
            Propmax = MeanFavProp + sd(FavProp)) %>%
  ungroup() %>%
  # RESTORED: Cytotoxic2 is 100% Unfavourable, so set FavProp to 0 instead of 1
  mutate(MeanFavProp = if_else(Therapy == 'Cytotoxic2', 0, MeanFavProp),
         Propmin = if_else(Therapy == 'Cytotoxic2', 0, Propmin),
         Propmax = if_else(Therapy == 'Cytotoxic2', 0, Propmax))

cdt_df_outcomes_wide <- cdt_df_outcomes %>%
  pivot_wider(names_from = Outcome, values_from = n) %>%
  replace(is.na(.), 0)

cdt_odds <- cdt_df_outcomes_wide %>%
  nest(data = c(-RepNum, -Therapy)) %>%
    mutate(fit = map(data, ~ glm(cbind(Unfavourable + 0.5, Favourable + 0.5) ~ ModelType, family = binomial, data = .)),
      mean.comp = map(fit, emmeans, ~ModelType, type = 'response'),
      odds.obj = map(mean.comp, pairs, reverse = T, simple = 'ModelType'),
      odds.ratio = map(odds.obj, tidy, conf.int = FALSE)) %>%
  unnest(odds.ratio) %>%
  select(RepNum, Therapy, contrast, odds.ratio) %>%
  group_by(contrast, Therapy) %>%
  summarise(MeanOdds = mean(odds.ratio),
            OddsMin = MeanOdds - sd(odds.ratio),
            OddsMax = MeanOdds + sd(odds.ratio)) %>% ungroup() %>%
  filter(contrast %in% c('(AC+Tr) / AC', '(SC+Tr) / SC', 'SC / AC', '(SC+Tr) / (AC+Tr)')) %>%
  mutate(contrast = factor(contrast, levels = c('SC / AC', '(SC+Tr) / SC', '(AC+Tr) / AC', '(SC+Tr) / (AC+Tr)')))

fig.cdt.odds <- ggplot(data = cdt_odds, aes(y = contrast)) +
  geom_point(aes(x = MeanOdds), size = 4) +
  geom_errorbarh(aes(xmin = OddsMin, xmax = OddsMax), linewidth = 1.4, height = 0.65) +
  facet_wrap(~ Therapy, nrow = 4, scales = 'free_x') +
  geom_vline(xintercept = 1, linewidth = 1.5, linetype = 'dashed', colour = 'red') +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 22), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 25), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 25), axis.title.x = element_text(size = 20)) +
  theme(strip.text = element_text(size = 25)) +
  labs(y = 'Comparison', x = 'Odds ratio')
ggsave('../figures/constant-dose/CDT-unfavourable-odds-ratios.png', fig.cdt.odds, dpi = 300, height = 9.5, width = 9)

cdt_outcomes_mean <- cdt_df_outcomes %>%
  group_by(ModelType, Therapy, Outcome) %>%
  summarise(MeanCount = mean(n), SD = sd(n)) %>%
  ungroup() %>%
  mutate(Outcome = factor(Outcome, levels = c("Unfavourable", "Favourable")))

fig.cdt.outcomes <- ggplot() +
  geom_bar(data = cdt_outcomes_mean, aes(fill=Outcome, x=ModelType, y=MeanCount), position = 'fill', stat = "identity") +
  # RESTORED: Plot MeanFavProp
  geom_pointrange(data = cdt_prop, aes(x=ModelType, y=MeanFavProp, ymin=Propmin, ymax=Propmax), linewidth = 1.5, size = 0.8) +
  facet_wrap(~Therapy, nrow = 2) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 15), legend.title = element_text(size = 20)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Proportion', x = 'Model Type')
ggsave('../figures/constant-dose/CDT-all-outcomes.png', fig.cdt.outcomes, dpi = 300, width = 8.5, height = 6.7)
```



## Adaptive therapy with no therapy controls
```{r data-import-at, message=FALSE, warning=FALSE}
st1_r1 <- read_csv("adaptive-therapy/AT-cytostatic-0.1-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st1_r1, 'Cytostatic1'); st1_r1 <- df$df; st1_r1$RepNum <- 1
st1_outcomes_r1 <- df$outcomes; st1_outcomes_r1$RepNum <- 1

st1_r2 <- read_csv("adaptive-therapy/AT-cytostatic-0.1-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st1_r2, 'Cytostatic1'); st1_r2 <- df$df; st1_r2$RepNum <- 2
st1_outcomes_r2 <- df$outcomes; st1_outcomes_r2$RepNum <- 2

st1_r3 <- read_csv("adaptive-therapy/AT-cytostatic-0.1-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st1_r3, 'Cytostatic1'); st1_r3 <- df$df; st1_r3$RepNum <- 3
st1_outcomes_r3 <- df$outcomes; st1_outcomes_r3$RepNum <- 3

st2_r1 <- read_csv("adaptive-therapy/AT-cytostatic-0.33-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st2_r1, 'Cytostatic2'); st2_r1 <- df$df; st2_r1$RepNum <- 1
st2_outcomes_r1 <- df$outcomes; st2_outcomes_r1$RepNum <- 1

st2_r2 <- read_csv("adaptive-therapy/AT-cytostatic-0.33-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st2_r2, 'Cytostatic2'); st2_r2 <- df$df; st2_r2$RepNum <- 2
st2_outcomes_r2 <- df$outcomes; st2_outcomes_r2$RepNum <- 2

st2_r3 <- read_csv("adaptive-therapy/AT-cytostatic-0.33-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(st2_r3, 'Cytostatic2'); st2_r3 <- df$df; st2_r3$RepNum <- 3
st2_outcomes_r3 <- df$outcomes; st2_outcomes_r3$RepNum <- 3

tx1_r1 <- read_csv("adaptive-therapy/AT-cytotoxic-0.01-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx1_r1, 'Cytotoxic1'); tx1_r1 <- df$df; tx1_r1$RepNum <- 1
tx1_outcomes_r1 <- df$outcomes; tx1_outcomes_r1$RepNum <- 1

tx1_r2 <- read_csv("adaptive-therapy/AT-cytotoxic-0.01-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx1_r2, 'Cytotoxic1'); tx1_r2 <- df$df; tx1_r2$RepNum <- 2
tx1_outcomes_r2 <- df$outcomes; tx1_outcomes_r2$RepNum <- 2

tx1_r3 <- read_csv("adaptive-therapy/AT-cytotoxic-0.01-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx1_r3, 'Cytotoxic1'); tx1_r3 <- df$df; tx1_r3$RepNum <- 3
tx1_outcomes_r3 <- df$outcomes; tx1_outcomes_r3$RepNum <- 3

tx2_r1 <- read_csv("adaptive-therapy/AT-cytotoxic-0.05-zero-delay-r1.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx2_r1, 'Cytotoxic2'); tx2_r1 <- df$df; tx2_r1$RepNum <- 1
tx2_outcomes_r1 <- df$outcomes; tx2_outcomes_r1$RepNum <- 1

tx2_r2 <- read_csv("adaptive-therapy/AT-cytotoxic-0.05-zero-delay-r2.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx2_r2, 'Cytotoxic2'); tx2_r2 <- df$df; tx2_r2$RepNum <- 2
tx2_outcomes_r2 <- df$outcomes; tx2_outcomes_r2$RepNum <- 2

tx2_r3 <- read_csv("adaptive-therapy/AT-cytotoxic-0.05-zero-delay-r3.csv", col_types = cols(...1 = col_skip()))
df <- plotdf(tx2_r3, 'Cytotoxic2'); tx2_r3 <- df$df; tx2_r3$RepNum <- 3
tx2_outcomes_r3 <- df$outcomes; tx2_outcomes_r3$RepNum <- 3

at_df <- bind_rows(st1_r1, st1_r2, st1_r3,
                    st2_r1, st2_r2, st2_r3,
                    tx1_r1, tx1_r2, tx1_r3,
                    tx2_r1, tx2_r2, tx2_r3)
at_df_outcomes <- bind_rows(st1_outcomes_r1, st1_outcomes_r2, st1_outcomes_r3, 
                             st2_outcomes_r1, st2_outcomes_r2, st2_outcomes_r3,
                             tx1_outcomes_r1, tx1_outcomes_r2, tx1_outcomes_r3,
                             tx2_outcomes_r1, tx2_outcomes_r2, tx2_outcomes_r3)
at_df_outcomes_wide <- at_df_outcomes %>%
  pivot_wider(names_from = Outcome, values_from = n) %>%
  replace(is.na(.), 0)
if(!"Unfavourable" %in% names(at_df_outcomes_wide)) at_df_outcomes_wide$Unfavourable <- 0
if(!"Favourable"   %in% names(at_df_outcomes_wide)) at_df_outcomes_wide$Favourable   <- 0
if(!"Cycling"      %in% names(at_df_outcomes_wide)) at_df_outcomes_wide$Cycling      <- 0
at_prop <- at_df_outcomes_wide %>%
  # RESTORED: Calculate FavProp
  mutate(FavProp = Favourable / (Unfavourable + Favourable + Cycling)) %>%
  group_by(ModelType, Therapy) %>%
  summarise(MeanFavProp = mean(FavProp),
            Propmin = MeanFavProp - sd(FavProp),
            Propmax = MeanFavProp + sd(FavProp)) %>%
  ungroup()
# RESTORED: Force standard stacking order so 'Cycling' is always top, Unfavourable middle, Favourable bottom
at_df_outcomes <- at_df_outcomes %>%
  mutate(Outcome = factor(Outcome, levels = c("Unfavourable", "Favourable", "Cycling")))
```

```{r cytostatic-bars, message=FALSE, warning=FALSE, echo=FALSE}
static <- at_df %>% filter((Therapy == 'Cytostatic1')|(Therapy == 'Cytostatic2'))
static_outcomes <- at_df_outcomes %>% filter((Therapy == 'Cytostatic1')|(Therapy == 'Cytostatic2'))
fig.static.outcomes <- ggplot(data = static_outcomes, aes(fill=Outcome, x=ModelType, y=n)) +
  geom_bar(position = 'fill', stat = "identity") +
  # RESTORED: Plot MeanFavProp
  geom_pointrange(data = at_prop %>% filter(Therapy %in% c('Cytostatic1', 'Cytostatic2')), 
                  aes(x=ModelType, y=MeanFavProp, ymin=Propmin, ymax=Propmax, fill=NULL), linewidth = 1.5, size = 0.8) +
  facet_wrap(~Therapy, nrow = 1) +
  custom_theme +
  scale_fill_manual(values = c("Cycling" = "#FF0000", "Unfavourable" = "#73D055FF", "Favourable" = "#2D708EFF")) +
  theme(axis.text.x = element_text(size=20, angle = 45, hjust = 1), axis.text.y = element_text(size = 25)) +
  theme(strip.text = element_text(size = 25)) +
  labs(y = 'Proportion', x = 'Model Type')

fig.static.rx <- ggplot(data = static, aes(fill = Outcome)) +
  geom_density(aes(x=r_x, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

fig.static.ry <- ggplot(data = static, aes(fill=Outcome)) +
  geom_density(aes(x=r_y, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

fig.static.a <- ggplot(data = static, aes(fill=Outcome)) +
  geom_density(aes(x=a, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

fig.static.b <- ggplot(data = static, aes(fill=Outcome)) +
  geom_density(aes(x=b, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

fig.static.c <- ggplot(data = static, aes(fill=Outcome)) +
  geom_density(aes(x=c, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

fig.static.d <- ggplot(data = static, aes(fill=Outcome)) +
  geom_density(aes(x=d, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

fig.static.delta <- ggplot(data = static, aes(fill=Outcome)) +
  geom_density(aes(x=delta, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) +
  labs(y = 'Density')

# FIX 3: Only ONE definition of fig.static.params (with delta).
# FIX 4: Removed labs(y='Frequency') from plot_annotation() — it is not a valid argument.
fig.static.params <- (fig.static.rx | fig.static.ry) /
                     (fig.static.c  | fig.static.d)  /
                     (fig.static.a  | fig.static.b)  /
                     (fig.static.delta | plot_spacer()) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = 'collect')

ggsave('../figures/adaptive-therapy/AT-cytostatic-parameter-distributions.png', fig.static.params, dpi = 300, width = 12, height = 11)

fig.static.outcomes
fig.static.rx; fig.static.ry; fig.static.c; fig.static.d; fig.static.a; fig.static.b

ggsave('../figures/adaptive-therapy/cytostatic-all-outcomes.png',      fig.static.outcomes, dpi = 300, width = 8.5, height = 6)
ggsave('../figures/adaptive-therapy/cytostatic-rx-distribution.png',   fig.static.rx,       dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytostatic-ry-distribution.png',   fig.static.ry,       dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytostatic-a-distribution.png',    fig.static.a,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytostatic-b-distribution.png',    fig.static.b,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytostatic-c-distribution.png',    fig.static.c,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytostatic-d-distribution.png',    fig.static.d,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytostatic-delta-distribution.png', fig.static.delta,   dpi = 300, width = 8.5, height = 5)
```

```{r cytotoxic-bars, message=FALSE, warning=FALSE, echo=FALSE}
toxic <- at_df %>% filter((Therapy == 'Cytotoxic1')|(Therapy == 'Cytotoxic2'))
toxic_outcomes <- at_df_outcomes %>% filter((Therapy == 'Cytotoxic1')|(Therapy == 'Cytotoxic2'))
fig.toxic.outcomes <- ggplot(data = toxic_outcomes, aes(fill=Outcome, x=ModelType, y=n)) +
  geom_bar(position = 'fill', stat = "identity") +
  # RESTORED: Plot MeanFavProp
  geom_pointrange(data = at_prop %>% filter(Therapy %in% c('Cytotoxic1', 'Cytotoxic2')), 
                  aes(x=ModelType, y=MeanFavProp, ymin=Propmin, ymax=Propmax, fill=NULL), linewidth = 1.5, size = 0.8) +
  facet_wrap(~Therapy, nrow = 1) +
  custom_theme +
  scale_fill_manual(values = c("Cycling" = "#FF0000", "Unfavourable" = "#73D055FF", "Favourable" = "#2D708EFF")) +
  theme(axis.text.x = element_text(size = 25, angle = 45, hjust = 1), axis.text.y = element_text(size = 25)) +
  labs(y = 'Proportion', x = 'Model Type')
fig.toxic.outcomes

fig.toxic.rx <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=r_x, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 30, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

fig.toxic.ry <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=r_y, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 30, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

fig.toxic.a <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=a, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

fig.toxic.b <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=b, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

fig.toxic.c <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=c, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

fig.toxic.d <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=d, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

fig.toxic.delta <- ggplot(data = toxic, aes(fill=Outcome)) +
  geom_density(aes(x=delta, after_stat(scaled)), alpha = 0.5, linewidth = 1) +
  facet_wrap(~Therapy, nrow = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15, angle = 45, hjust = 1), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(legend.text = element_text(size = 10), legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15)) + labs(y = 'Density')

# FIX 4: Removed labs(y='Frequency') from plot_annotation()
fig.toxic.params <- (fig.toxic.rx | fig.toxic.ry) /
                    (fig.toxic.c  | fig.toxic.d)  /
                    (fig.toxic.a  | fig.toxic.b)  /
                    (fig.toxic.delta | plot_spacer()) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = 'collect')

ggsave('../figures/adaptive-therapy/AT-cytotoxic-parameter-distributions.png', fig.toxic.params, dpi = 300, width = 12, height = 11)

fig.toxic.outcomes
fig.toxic.rx; fig.toxic.ry; fig.toxic.c; fig.toxic.d; fig.toxic.a; fig.toxic.b

ggsave('../figures/adaptive-therapy/cytotoxic-all-outcomes.png',       fig.toxic.outcomes, dpi = 300, width = 8,   height = 6)
ggsave('../figures/adaptive-therapy/cytotoxic-delta-distribution.png', fig.toxic.delta,    dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytotoxic-rx-distribution.png',    fig.toxic.rx,       dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytotoxic-ry-distribution.png',    fig.toxic.ry,       dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytotoxic-a-distribution.png',     fig.toxic.a,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytotoxic-b-distribution.png',     fig.toxic.b,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytotoxic-c-distribution.png',     fig.toxic.c,        dpi = 300, width = 8.5, height = 5)
ggsave('../figures/adaptive-therapy/cytotoxic-d-distribution.png',     fig.toxic.d,        dpi = 300, width = 8.5, height = 5)
```

```{r odds-ratio-at, message=FALSE, warning=FALSE}
at_favprop <- at_df_outcomes_wide %>%
  mutate(FavProp = Favourable / (Unfavourable + Favourable + Cycling)) %>%
  group_by(ModelType, Therapy) %>%
  summarise(MeanFavProp = mean(FavProp),
            Propmin = MeanFavProp - sd(FavProp),
            Propmax = MeanFavProp + sd(FavProp)) %>%
  ungroup()

at_odds <- at_df_outcomes_wide %>%
  nest(data = c(-RepNum, -Therapy)) %>%
  # Clean GLM with pseudocounts
  mutate(fit = map(data, ~ glm(cbind(Unfavourable + 0.5, Favourable + Cycling + 0.5) ~ ModelType, family = binomial, data = .)),
      mean.comp  = map(fit, emmeans, ~ModelType, type = 'response'),
      odds.obj   = map(mean.comp, pairs, reverse = T, simple = 'ModelType'),
      odds.ratio = map(odds.obj, tidy, conf.int = FALSE)) %>%
  unnest(odds.ratio) %>%
  select(RepNum, Therapy, contrast, odds.ratio) %>%
  group_by(contrast, Therapy) %>%
  summarise(MeanOdds = mean(odds.ratio),
            OddsMin = MeanOdds - sd(odds.ratio),
            OddsMax = MeanOdds + sd(odds.ratio)) %>% ungroup() %>%
  filter(contrast %in% c('(AC+Tr) / AC', '(SC+Tr) / SC', 'SC / AC', '(SC+Tr) / (AC+Tr)')) %>%
  mutate(contrast = factor(contrast, levels = c('SC / AC', '(SC+Tr) / SC', '(AC+Tr) / AC', '(SC+Tr) / (AC+Tr)')))

fig.at.odds <- ggplot(data = at_odds, aes(y = contrast)) +
  geom_point(aes(x = MeanOdds), size = 4) +
  geom_errorbarh(aes(xmin = OddsMin, xmax = OddsMax), linewidth = 1.4, height = 0.65) +
  facet_wrap(~ Therapy, nrow = 4, scales = 'free_x') +
  geom_vline(xintercept = 1, linewidth = 1.5, linetype = 'dashed', colour = 'red') +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 25), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 25), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  theme(strip.text = element_text(size = 20)) +
  labs(y = 'Comparison', x = 'Odds ratio')
ggsave('../figures/adaptive-therapy/AT-unfavourable-odds-ratios.png', fig.at.odds, dpi = 300, height = 9.5, width = 8)

```{r frequency-plots, message=FALSE, warning=FALSE}
# FIX 1: Use is.finite() consistently — no more != 'Inf' string comparisons
all_therapy <- at_df %>% rename(Frequency = Period)

fig.freqdist <- ggplot(data = all_therapy %>% filter(is.finite(Frequency)),
                       mapping = aes(x = ModelType, y = Frequency)) +
  geom_boxplot(alpha = 0.5, linewidth = 1, outliers = F) +
  stat_boxplot(geom = "errorbar", width = 0.5, position = position_dodge(0.9)) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  labs(y = 'Period (h)')
fig.freqdist
ggsave('../figures/adaptive-therapy/AT-period-distributions-cytotoxic2-only.png', fig.freqdist, dpi = 300)

fig.cycling.rx <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=r_x), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_blank(), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_blank()) +
  labs(y = 'r_x')
ggsave('../figures/adaptive-therapy/AT-cycling-rx-dist.png', fig.cycling.rx, dpi = 300)

fig.cycling.ry <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=r_y), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_blank(), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_blank()) +
  labs(y = 'r_y')
ggsave('../figures/adaptive-therapy/AT-cycling-ry-dist.png', fig.cycling.ry, dpi = 300)

fig.cycling.c <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=c), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_blank(), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_blank()) +
  labs(y = 'c')
ggsave('../figures/adaptive-therapy/AT-cycling-c-dist.png', fig.cycling.c, dpi = 300)

fig.cycling.d <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=d), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_blank(), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_blank()) +
  labs(y = 'd')
ggsave('../figures/adaptive-therapy/AT-cycling-d-dist.png', fig.cycling.d, dpi = 300)

fig.cycling.a <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=a), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  labs(y = 'a')
ggsave('../figures/adaptive-therapy/AT-cycling-a-dist.png', fig.cycling.a, dpi = 300)

fig.cycling.b <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=b), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  labs(y = 'b')
ggsave('../figures/adaptive-therapy/AT-cycling-b-dist.png', fig.cycling.b, dpi = 300)

fig.cycling.delta <- ggplot(data = all_therapy %>% filter(is.finite(Frequency))) +
  geom_violin(aes(x=ModelType, y=delta), alpha = 0.5, linewidth = 1) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  labs(y = 'delta')
ggsave('../figures/adaptive-therapy/AT-cycling-delta-dist.png', fig.cycling.delta, dpi = 300)

# FIX 4: Removed labs(y='Frequency') from plot_annotation()
fig.cycling.allparams <- ((fig.cycling.rx | fig.cycling.ry) /
                          (fig.cycling.c  | fig.cycling.d)  /
                          (fig.cycling.a  | fig.cycling.b)  /
                          (fig.cycling.delta | plot_spacer())) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(axes = 'collect_x', axis_titles = 'collect_x')
fig.cycling.allparams
ggsave('../figures/adaptive-therapy/AT-cycling-all-parameters.png', fig.cycling.allparams, dpi = 300, height = 10, width = 8)
```

```{r at-cycling-effsizes, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
cycling_comp <- at_df %>%
  # 1. CRITICAL FIX: Only analyze the therapy that actually produces cycles!
  filter(Therapy == 'Cytotoxic2') %>%
  mutate(Outcome = if_else(Outcome == 'Cycling', 'Cycling', 'NotCycling'))

cycling.effect.size <- cycling_comp %>%
  pivot_longer(cols = r_x:delta, names_to = 'Parameter') %>%
  select(ModelType, Parameter, value, RepNum, Outcome) %>%
  nest(data = c(-RepNum, -ModelType, -Parameter)) %>%
  # 2. CRITICAL FIX: Only run cohens_d if there are exactly 2 groups to compare
  mutate(effsize.obj = map(data, ~ if(length(unique(.x$Outcome)) > 1) rstatix::cohens_d(.x, value ~ Outcome) else NULL)) %>%
  unnest(effsize.obj) %>%
  select(ModelType, Parameter, RepNum, effsize) %>%
  drop_na()

effsize.plotdf <- cycling.effect.size %>%
  group_by(ModelType, Parameter) %>%
  summarise(EffSize = mean(effsize),
            Emin = EffSize - sd(effsize),
            Emax = EffSize + sd(effsize)) %>%
  ungroup()

fig.effsize.cycling <- ggplot(data = effsize.plotdf, aes(y = ModelType, x = EffSize)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = Emin, xmax = Emax), linewidth = 1.2, height = 0.5) +
  geom_vline(xintercept = 0, linewidth = 1.5, linetype = 'dashed', colour = 'red') +
  facet_wrap(~Parameter, nrow = 3) +
  theme(axis.ticks.y = element_line(linewidth = 1.5), axis.text.y = element_text(size = 15), axis.ticks.length.y = unit(0.25, "cm")) +
  theme(axis.ticks.x = element_line(linewidth = 1.5), axis.text.x = element_text(size = 15), axis.ticks.length.x = unit(0.25, "cm")) +
  theme(axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  labs(x = "Cohen's d (Cycling vs NotCycling)", y = 'Model Type')
ggsave('../figures/adaptive-therapy/AT-cycling-effect-sizes.png', fig.effsize.cycling, dpi = 300, width = 10, height = 8)
